---
output: github_document
html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  fig.path = "README-"
)
```

### RingR
***

`RingR` is a simple tool to circumvent manual data entries using software `Ring 2.0` to submit bird ringing data to the IFV Helgoland. *This is not a ready-to-use package, but rather a starting point for anyone with some experience in programming in R to avoid using another software to export data which is already well curated in the database of the user*.  


*The package is available as follows*

```{r, eval=FALSE}
if (!("devtools" %in% rownames(installed.packages()))) {
  install.packages("devtools")
} else if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("mottensmann/RingR")
```

Currently, the package contains a few functions to create and check export files:

* `export.ring`: Export ringing data
* `check.ring`: check export file
* `read.lookup`: Open lookup table
* `place.suggest`: Get suggested place names based on topographic name and Tk25 number

See the respective helpfiles if you are interested in these functions to your own data

```{r, fig.align='left', echo=FALSE}
load("Map.RData")
comb[[1]] 
knitr::kable(comb[[2]][,c("No", "Code")],
                  row.names = FALSE,
                  col.names = c("Number", "strPlaceCode"),
                  format = "html")
```
